\clearpage
\pagenumbering{roman} 				
\setcounter{page}{1}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\chaptermark}[1]{\markboth{\chaptername\ \thechapter.\ #1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\renewcommand{\headrulewidth}{0.1ex}
\renewcommand{\footrulewidth}{0.1ex}
\fancyfoot[LE,RO]{\thepage}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[LE,RO]{\thepage}\renewcommand{\headrulewidth}{0ex}}

\section*{\Huge Summary}


\noindent 
Machine learning methods based on deep convolutional neural networks (CNN’s) have in recent years came to dominate the state of the art in object recognition. Huge research efforts are currently being devoted to this field, and new network architectures are frequently being proposed. For the particular task of detection of ships in images, these networks must be trained on an appropriate set of annotated images. As these tasks, which are somewhat labor intensive, will have to be repeated many times as new networks and improvements appear, a systematic and reusable framework is highly desirable. To develop this is the goal of this master thesis. In particular, the thesis addresses the following:

\begin{enumerate}
    \item Conduct a literature survey on methods for detection of ships in camera images. In particular, the survey should discuss the rationale for the recent popularity of deep learning techniques, include the most popular CNN approaches, and discuss other machine learning approaches.
    \item Develop a complete framework for training and testing, so that both training and testing on new image sets can be done with minimal efforts for popular networks. While the training can accept unordered collections of individual images, it is important that the testing can work on video streams, so that temporal detection metrics can be investigated. 
    \item Train and test the detection algorithms Yolo and SSD on real data
    \item Write report and discuss strengths and weaknesses for both of the networks, and also for different training and testing sets.
\end{enumerate}

\clearpage